### 2022-02-21 rebuttal/rebuttal-letter/trunk-rebuttal.tex

	\lreviewer{line 249}{v1:2.10}{Use of the word 'range' for the 'navy range' type of use is intermixed with range as in distance. Suggest not using 'range' and in 'navy range' and saying 'nav' or 'comms' system or network.}

	We have adopted this suggestion and use navigation or communication system instead.

@@

	\lreviewer{line 261}{v1:2.11}{'bring'. Do you mean interpolate?}
	Yes. We have changed this accordingly.

	\lreviewer{line 281}{v1:2.12}{Awkward sentence, either unclear or extremely obvious. "...an acoustic arrival does not always take the direct path from source to the receiver,".}

	We have removed this sentence in favor of discussing ray refraction and reflection.

@@

	\lreviewer{}{}{for both criteria: a graphic that shows the method could be very useful.}

	This is a good point. We hope that the separation of MBC and NBC, as well as the extended discussion in Section III-C, better illustrate both criteria. A visual on its own would be quite similar to the eigenray plots added. However, we are happy to include a graphic showing the method if reviewers find the narrative explanation lacking.

@@

	\lreviewer{line 319}{v1:2.14}{"This is likely driven by the prominence of the duct." Do you mean: consistency of sound speed within the duct where the rays were trapped and thus traveled? Or something else?}

	We mean prominence, often used in peak finding, which would indicate both the considerable sound speed differential and the nearly horizontal slope to the local maxima. This is now explained more clearly and introduced early at line \ref{v1:2.5}.

@@

	{\color{blue} Thank you for this suggestion. We have deleted the table and instead summarized the issue.}

	\lreviewer{lines 585-591}{}{Suggest deleting, not very appropriate for an academic paper.}

	This has been removed.

	\lreviewer{Fig 10}{v1:fig:gvel-post}{Would be good to have some conclusions in addition to the description.}

	This figure has been condensed into the main body of the text alongside conclusions around the effective sound speed estimation.

@@

%% ------- COMMENTS FROM EDITOR ------ %%
\section{Comments from the Editor}

	\reviewer{}
	{Both reviewers recommend that the manuscript be reconsidered after revision based on the reviews, and I concur. The key point of the manuscript seems to be to compare two different approaches to determining an effective sound speed for converting travel times to ranges for use in determining positions by trilateration in an Arctic environment (designated Minimal Bounce Criteria and Nearest Bounce Criteria). The goal is not evident in the abstract and is first more-or-less (but not entirely) clearly stated in Section II (Methods) (lines 174-176). While some discussion of the AUV operations is appropriate to motivate the analysis, the extensive discussion in the Introduction and elsewhere in the manuscript seems unnecessary and inappropriate. The use of jargon from the AUV application (e.g., physical layer, virtual layer) also seems unnecessary.}

	Thank you. The key point of this paper is a model-aided component to the LBL paradigm that we demonstrated in the Beaufort Sea. 
	Because both reviewers and the editor felt the key points were comparing the two different approaches to determine an effective sound speed for converting travel times to ranges, we have significantly restructured the paper to make the narrative clearer.

@@

	The discussion of AUV operations and jargon from AUV application contextualizes the model-aided component to the LBL paradigm. However, we agree with the Editor that this emphasis can be distracting when used throughout the manuscript.
	We have attempted to use the most direct language possible in each section.
	We hope this revision presents the contributions more clearly and welcome further feedback on this matter.

	\reviewer{}
	{I agree with Reviewer 1 that the manuscript needs much more information on the acoustic parameters (frequencies, pulse lengths/modulation, ranges, expected travel-time measurement accuracy, etc.).

	In addition, the ray geometries are quite different for cases in which the source and receiver are both in the surface duct (i.e., 20 and 30 m), both in the Beaufort Duct (for the sound-speed profiles for which it is present) (i.e., 90 m) and one of the source or receiver is in the surface duct and the other is in the Beaufort Duct. The manuscript needs to include some discussion of these different cases.}

	We have now included the information on acoustic parameters in the experiment description. We apologize that this information was ommitted as the manuscript was adapted from a thesis.

	Similarly, we have addressed the editor's point about the ray geometries in Section III-C (see comments, but have opted to keep those figures in the supplementary material.

	Comment \ref{1dot6} is relevant to both of these points.

@@

	\reviewer{}
	{Why is the effective sound-speed determined from the GPS-determined range and the acoustic travel time referred to as “… the naïve group velocity …”? What is naïve about it?}

	We have recast this as ``implied effective horizontal sound speed'', as per comment \ref{1dot5}.

	\reviewer{}
	{Figure 3 is only referenced in the Fig. 4 caption.}

	Thank you for catching this. We have corrected it and made sure all figures are referenced in the text directly.

	\reviewer{}
	{I agree with both reviewers that the Section IV.E, GPS sensor drift at polar latitudes, is out of place. I find the term “GPS drift” itself odd. It seems that the authors really mean GPS accuracy.} \label{3dot7}

	We have talked with colleagues and think ``GPS noise'' is the best term. But given that all reviewers and the editor feel this section is out of place, we have significantly reduced it. Please see comment \ref{2dot3}.

	\reviewer{}
	{The statement (or similar statements) made in various places in the manuscript that “… we present a working solution for underwater navigation that achieves GPS-like accuracy and precision …” (lines 120-121) is not a quantitative or meaningful statement. GPS (really GNSS) applications come in different flavors, including stand-alone single frequency, stand-alone dual frequency, differential, real-time kinematic, etc., with varying accuracies.}

	When evaluating our methodology and results, we have removed qualitative language like ``GPS-like'' or ``rivaling GPS'' in favor of quantitative descriptions of ranging error, i.e., achieving ``x`` accuracy compared to ''y`` from the GPS unit''.

@@

	\reviewer{}
	{Unsupported generalizations about previous work, e.g., “… conversion of travel time into range … is an often overlooked element of any underwater navigation system …” (lines 174-176) are to be avoided. In this case, the generalization is in fact incorrect.}

	Thank you. We have removed this generalization.

	\reviewer{}
	{Several of the references are incomplete, i.e., Norgren et al. (2014), Poulsen et al. (2016), Schmidt and Schneider (2016), and Schneider et al. (2020).}

	Thank you for pointing this out. We have double checked all references.

@@

%% ------- REVIEWER QUESTIONS ------- %%

\section{Reviewer's Responses to Questions}

	\reviewer{}{Is the manuscript of good scientific quality, free from errors, misconceptions or ambiguities; does it present original work; and does it contain sufficient new results, new applications or new developments of reasonable enough significance to warrant its publication in JASA? Please indicate in your report (in detailed comments, below) any points which are objectionable or which need attention.}
	\textbf{Reviewer 1:} It presents original work.  There are aspects which need clarification and are outlined in the attached report.

	\textbf{Reviewer 2:} The work is interesting and describes a data set collected from the Arctic, which is of high value. However, some of the writing is a bit awkward and occasionally vague or imprecise.

@@

	Thank you for the pointed feedback. We hope you find this revision clearer and more precise.

	\reviewer{}{Is JASA an appropriate journal in which to present this work? In this regard, please consider carefully the commitment of JASA to publish work that is within the scope of Acoustics. Does the content of the manuscript, including terminology and the references cited, meet this criterion?}

	{\textbf{Reviewer 1:} I wouldn’t say JASA is the most appropriate journal.  As written, this work might be better suited to an ocean engineering journal. The results do, however, rely on acoustic propagation models which does make it fall within the scope of JASA, and it is particularly applicable to the Arctic Acoustics special issue.  I've made some suggestions in the attached (e.g., I didn't see that the frequency of the acoustic transmissions was  mentioned.  That is something that should be mentioned for an acoustics audience).

	\textbf{Reviewer 2:} Yes.}

@@

	Thank you. We hope this manuscript would be of relevance to the Arctic Acoustics special issue given two topics of interest: under-ice navigation systems for floats, gliders, and autonomous underwater vehicles, and comparisons of current Arctic acoustic conditions with historical data.

	\reviewer{}{Is the manuscript a clear, concise, reasonably self-contained presentation of the material, giving adequate references to related work? Is English satisfactory? Please indicate needed changes in your report.}
	{\textbf{Reviewer 1:} The English is satisfactory.  This paper could benefit from some reorganization and careful editing. Several references to figures and tables were missing or incomplete. The hypothesis was presented in the discussion, but could be improved if this was more clearly stated at the outset.  Please see attached report for specific comments and suggestions.

	\textbf{Reviewer 2:} Overall the language is fine, details below.}

@@

	Thank you. We have significantly reorganized the paper.

	\reviewer{}{Are the tables and figures clear and relevant, and are the captions adequate? Are there either too many or too few? If any of the figures are in color, is the color essential for conveying the scientific point?}
	{\textbf{Reviewer 1:} I would suggest combining Figures 1 and 2 or eliminating Figure 1.  Some suggestions for improving figure and table titles and captions are in the attached report.  The use of color does help convey the scientific point.

	\textbf{Reviewer 2:} In general they are fine except as noted.}

	\reviewer{}{If Supplementary material was submitted, is it relevant to the manuscript and should it be deposited in the Supplemental Depository for reference to the manuscript?}
	{\textbf{Reviewer 1:} The supplemental figures were relevant to the manuscript.

	\textbf{Reviewer 2:} NA}

	\reviewer{}{Does the paper make effective use of journal space, or are parts unnecessary, unimportant, or subject to condensation? If so, which?
	}
	{\textbf{Reviewer 1}: I'd suggest condensing the section on GPS drift (Section III E).

	\textbf{Reviewer 2}: The GPS section seems out of place. Can it be shortened to a few sentences and references?}

@@

	We have significantly condensed the background for this section and narrowed the discussion for this section about the pattern of psuedorange error and what it might mean for the precision of the GPS puck we used at high latitudes.

	\reviewer{}{
	Is the title appropriate and the abstract adequate for verbatim reproduction in abstract journals? IMPORTANT: The lead paragraph should advertise the main points of the article and must describe in terms accessible to the general reader the context and significance or the research problem studied and the importance of the results.}
	{\textbf{Reviewer 1}: The title and abstract are a bit misleading as there is no navigation demonstrated in the paper and the ranging results were from fixed buoys rather than a vehicle.  The abstract, and the final sentence in particular, should be tempered to reflect the scope of the results.  Also, the abstract specifies absolute error of 11m, but should note the range over which it’s measured.  The lead paragraph does not advertise the main points of the article.

	\textbf{Reviewer 2}: Title, yes.
	The abstract does need some work. Statements like this are risky, suggest summarizing technical contributions.
	\begin{quote}
	To our knowledge, these results are the first field experiment to demonstrate a real-time, physics-based data processing to minimize ranging error in underwater navigation.
	\end{quote}}

	Thank you. We have opted to keep the title the same, as we have now integrated results from the AUV instead of allowing beacon results to serve as a proxy for navigation writ large.
